Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-03-27 paper.tex
update

\appendix
\section{jets parameter variations}
\textcolor{red}{KY: Please also add a section (either in the Discussion
or Appendix) to discuss about the parameter variations.
I think the figures you showed me are very important
and informative.}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}
\raggedright
\caption{Jet parameters.}
\label{tablb-jet-parameters}
\begin{tabular}{@{}llllllll@{}}
\toprule[1pt]\midrule[0.3pt]
                  & A          & B          & C          & D          & E          & F          & G          \\ \midrule
$k_{B}T$ (MeV)    & 1.720      & 17.200     & 1.720      & 0.172      & 1.720      & 1.720      & 1.720      \\
$\rho$ (g/cm$^3$) & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-25}$ & $10^{-27}$ & $10^{-26}$ \\
$\beta\gamma$     & 1.2        & 0.6        & 0.6        & 0.6        & 0.6        & 0.6        & 0.3        \\ \midrule
\end{tabular}
\end{table*}

>>>>

\appendix
\section{jets parameter variations}

\textcolor{red}{KY: Please also add a section (either in the Discussion
or Appendix) to discuss about the parameter variations.
I think the figures you showed me are very important
and informative.}

In this section, we present the simulation results using exactly same parameters\
except for the density ($\rho$), temperature ($k_{B}T$),\
and four-velocity ($\beta\gamma$) within the jet source.\
These variable parameters, including the fiducial run (C), are\
tabulated in Table \ref{tablb-jet-parameters} and visualized in Fig. \ref{fig__jet_parameters}.

\begin{table*}
\raggedright
\caption{The list of runs showing different injected jet parameters.\
         The fiducial run (C) has been pointed out by an asterisk in the list. }
\label{tablb-jet-parameters}
\begin{tabular}{@{}llllllll@{}}
\toprule[1pt]\midrule[0.3pt]
                  & A          & B          & C*         & D           & E          & F          & G          \\ \midrule
$k_{B}T$ (MeV)    & 1.720      & 0.172      & 1.720      & 17.200      & 1.720      & 1.720      & 1.720      \\
$\rho$ (g/cm$^3$) & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-26}$  & $10^{-25}$ & $10^{-27}$ & $10^{-26}$ \\
$\beta\gamma$     & 1.2        & 0.6        & 0.6        & 0.6         & 0.6        & 0.6        & 0.3        \\ \midrule
\end{tabular}
\end{table*}
